Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-09 paper-kelompok/main.tex
Modify UI images

\subsection{User Interface}
The first page of the spectrum-mode measurement instructs the user to insert the blank reference sample into the DMF system.
The sample input page, which resembles the blank input page, will be on the next page.
A result page with the peak wavelength and absorbance results will show up after the other subsystems have finished measuring absorbance.
The user has the option to save the result, return to the main menu, or view the entire spectrum of the absorbance measurement.
Fig. \ref{lcd-spectrum} illustrates how the spectrum page of the absorbance measurement is shown.

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
    \caption{The display of the spectrum page of a spectrum-mode measurement}
    \label{lcd-spectrum}
    \end{figure}

Quantization-mode measurement starts with a page that displays the list of saved curves.
Users have the option of using, removing, or adding new curves.
The user will get a table page if they select an existing curve.
The table consists of concentration and absorbance values of standard samples, as shown in Fig. \ref{lcd-table}.
By moving the pointer to the desired absorbance (A) cell and clicking the OK physical button, an absorbance measurement for each concentration value should be made.
The user will be directed to the blank and sample input page.
The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot.

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-table}
    \end{figure}

>>>>

\subsection{User Interface}
The first page of the spectrum-mode measurement instructs the user to insert the blank reference sample into the DMF system.
The sample input page, which resembles the blank input page, will be on the next page.
A result page with the peak wavelength and absorbance results will show up after the other subsystems have finished measuring absorbance.
The user has the option to save the result, return to the main menu, or view the entire spectrum of the absorbance measurement.
Fig. \ref{lcd-spec} illustrates how the result and spectrum page of the absorbance measurement is shown.

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-spec.JPEG}}
    \caption{The display of the result pages of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

Quantization-mode measurement starts with a page that displays the list of saved curves.
Users have the option of using, removing, or adding new curves.
The user will get a table page if they select an existing curve.
The table consists of concentration and absorbance values of standard samples, as shown in the left side of Fig. \ref{lcd-conc}.
By moving the pointer to the desired absorbance (A) cell and clicking the OK physical button, an absorbance measurement for each concentration value should be made.
The user will be directed to the blank and sample input page.
The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-conc.JPEG.}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}
